I/O simulation model with Linux page cache, integration and evaluation in SimGrid framework

### 2020-10-27 paper_io_sim.tex
Update figures

\author{\IEEEauthorblockN{Hoang-Dung Do, Val\'erie Hayot-Sasson, Tristan Glatard
  }\\
  \IEEEauthorblockA{
    Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada
  }
}

@@

			This longer read can be explained with the amount of cached data of files 
			at the beginning of the read in reality and simulators shown in 
			Figure~\ref{fig:single_cache}. 			
			In this figure, \textit{file$<$i$>$} is the input of \textit{read$<$i$>$} and 
			output of \textit{write$<$i-1$>$}. 
			In the real execution, after \textit{write2}, which writes \textit{file3}, 
			all data of \textit{file3} is in cache (Figure~\ref{fig:fincore_real}). 
			Thus, in \textit{read3}, \textit{file3} is read with memory bandwidth. 
			But in our simulator, after \textit{write2}, only a part of \textit{file3} 
			remains in cache (Figure~\ref{fig:fincore_wrench}). 
			The reason is while \textit{file3}  is being written, the page cache is saturated, 
			eviction is then evoked to evict data from page cache, make space 
			available for \textit{file3}. 
			However, because the evicted amount is less than required, 
			some \textit{file3} data is evicted after being written, make \textit{file3} 
			partially cached. 
			As a result, in \textit{read3}, only a part of \textit{file3} is read from cache 
			with memory bandwidth, a part of it is read from disk with disk read bandwidth, 
			which is many times slower, leading to longer read time.

>>>>

\author{\IEEEauthorblockN{Hoang-Dung Do, Val\'erie Hayot-Sasson, Rafael Ferreira da Silva, Henri Casanova, Tristan Glatard
  }\\
  \IEEEauthorblockA{
    Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada
  }
}

@@

			This longer read can be explained with the amount of cached data of files 
			at the beginning of the read in reality and simulators shown in 
			Figure~\ref{fig:single_cache}. 			
			In this figure, \textit{file $<$i$>$} is the input of \textit{Read $<$i$>$} and 
			output of \textit{Write $<$i-1$>$}. 
			In the real execution, after \textit{Write 2}, which writes \textit{file 3}, 
			all data of \textit{file 3} is in cache. 
			Thus, in \textit{Read 3}, \textit{file 3} is read with memory bandwidth. 
			But in our simulator, after \textit{Write 2}, only a part of \textit{file 3} 
			remains in cache. 
			The reason is while \textit{file 3}  is being written, the page cache is saturated, 
			eviction is then evoked to evict data from page cache, make space 
			available for \textit{file 3}. 
			However, because the evicted amount is less than required, 
			some \textit{file 3} data is evicted after being written, make \textit{file 3} 
			partially cached. 
			As a result, in \textit{Read 3}, only a part of \textit{file 3} is read from cache 
			with memory bandwidth, a part of it is read from disk with disk read bandwidth, 
			which is many times slower, leading to longer read time.
